Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

%work in progress / noch nicht fertig
Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and scanning
confocal microscopy (SCM). This combination enables simultaneous SICM and FM imaging of
the same region, in this case the surface, of the same sample at the same time. To achieve matching
field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
two slightly different setups are imaginable and have been put to the test (see figure 
\ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.

@@

As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
corresponding data point in the other set. This immediate correlation allows not only for correlating
studies in fixed samples (figure \ref{fig:sicm+scm}c), but also studies of dynamics in live samples 
(figure \ref{fig:sicm+scm}d).

To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating the
dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells 
(figure \ref{fig:sicm+scm}d), for the investigating the uptake of fluorescent nanoparticles in 
immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells \cite{Kemp2008} and for 
investigating the differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been utilized
in studies investigating endocytotic pathways \cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and in
a study investigating an alternative closing mechanism for clathrin-coated pits (CCPs) by recording 
topography simultaneously with the fluorescence of actin-binding protein-green fluorescent protein 
(Abp1-GFP) and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}.
In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized human
alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.

>>>>

Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and scanning
confocal microscopy (SCM). This combination enables simultaneous SICM and FM imaging of
the same region, in this case the surface, of the same sample at the same time. To achieve matching
field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
two slightly different setups are imaginable and have been put to the test (see figure 
\ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.

@@

As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
corresponding data point in the other set. This immediate correlation, schematically illustrated in
figure \ref{fig:sicm+scm}a, allows not only for correlating studies in fixed samples (figure 
\ref{fig:sicm+scm}c), but also studies of dynamics in live samples (figure \ref{fig:sicm+scm}d).

To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating the
dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells 
(figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent nanoparticles in 
immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells \cite{Kemp2008} and for 
investigating the differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been utilized
in studies investigating endocytotic pathways \cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and in
a study investigating an alternative closing mechanism for clathrin-coated pits (CCPs) by recording 
topography simultaneously with the fluorescence of actin-binding protein-green fluorescent protein 
(Abp1-GFP) and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}.
In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized human
alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.
